---
title: "REDCap - Parameterized Report"
author: "CCHMC RUG"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: journal
    highlight: breezedark
    toc: TRUE
    toc_float: TRUE
    code_folding: hide
params:
  id:
    label: "ID"
    value: 101
    input: select
    choices: [101, 102, 105, 106, 120]
    multiple: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, comment = NA)
```

```{r lib, echo = FALSE}
library(tidyverse)
```

```{r token, echo = FALSE}
cchmc_rug_token <- Sys.getenv("cchmc_rug_token")
```

```{r body, echo = FALSE}
post_body <- list(
  token                       = cchmc_rug_token,
  content                     = 'record',
  format                      = 'csv',
  type                        = 'flat',
  rawOrLabel                  = 'raw'
)
```

SSL Validation:

```{r verify, echo = FALSE}

ssl_verify <- httr::POST(
  url                         = 'https://redcap.research.cchmc.org/api/',
  body                        = post_body,
  config                      = httr::config(ssl_verifypeer=TRUE)
)

ssl_verify[2]
```

```{r pull, echo = FALSE}

redcap_pull <- httr::POST(
  url = 'https://redcap.research.cchmc.org/api/',
  body = post_body
)

```

```{r data, echo = FALSE}

redcap_data <- httr::content(redcap_pull)

```

# Report Description

This report summarizes dummy data from participants with oral glucose tolerance test (OGTT) results. The first part creates a summary table with anthropometric information (height, weight, BMI), age, and test related information.  The second part of this report visualizes each participant's individual OGTT results.

# Participant OGTT Results

This report contains the data from the following IDs:

```{r param_filter, echo = FALSE}

d <- filter(redcap_data, id %in% params$id)

# print IDs of particpants in report
p <- params$id
p 

```

## Summary Table

```{r summary}

d_summary <- d %>% 
  mutate(BMI = weight_kg/(height_cm/100)^2,
         age_at_test = round((test_date - dob)/365.25, digits = 1),
         age_at_test = as.numeric(age_at_test)) %>% 
  select(ID = id,
         DOB = dob,
         `Age at Test` = age_at_test,
         `Test Date` = test_date,
         `Weight (kg)` = weight_kg,
         `Height (cm)` = height_cm,
         BMI,
         `OGTT Fasting` = ogtt_0,
         `OGTT 1HR` = ogtt_10,
         `OGTT 2HR` = ogtt_20)

knitr::kable(d_summary, format = "html") %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))

```

```{r d_ogtt}

d_ogtt <- d %>% 
  pivot_longer(ogtt_0:ogtt_25, names_to = "ogtt_var", values_to = "ogtt_value") %>% 
  separate(col = ogtt_var, into = c("ogtt", "ogtt_interval")) 

d_ogtt <- d_ogtt %>% 
  mutate(ogtt_interval = as.numeric(ogtt_interval)/10) %>% 
  select(-ogtt)

```

## OGTT Plot

```{r plot}

ogtt_plot_f <- function(param_id) {
 
  d_plot <- filter(d_ogtt, id %in% param_id)
  
  ggplot(d_plot, aes(ogtt_interval, ogtt_value)) +
    geom_point(aes(color = as.factor(ogtt_interval),
                   text = paste('ID:', id,
                                '<br>OGTT Value:', ogtt_value,
                                '<br>Interval:', ogtt_interval, "HRS")),
               size = 2) +
    geom_line(alpha = 0.25) +
    theme(legend.position = "none") +
    xlab("OGTT Interval (HRS)") +
    ylab("OGTT Value (mg/dL)") +
    ggtitle(paste("Participant", param_id))
  
  #plotly::ggplotly(ogtt_plot, tooltip = "text")
}

map(unique(d$id), ogtt_plot_f)

```

```{r}
### test code for plotly

#map(unique(d$id), ogtt_plot_f)
#p_list <- map(101:110, ogtt_plot_f)

#plotly_list <- map(p_list, plotly::ggplotly)

# plotly_list[[1]]
# plotly_list[[2]]

#p_list_vector <- 1:length(p_list)

# for (i in seq_along(p_list_vector)) {
# 
#         plot <- p_list[[i]]
#         pplot <- plotly::ggplotly(plot, tooltip = "text")
#         print(pplot)
# }
```

